---
title: "P8105 Homework 1"
author: "Shiyu Kang"
output: github_document
---

# Problem 1

```{r problem1}
library(ggplot2)
data("penguins", package = "palmerpenguins")
```
The penguins table contains `r nrow(penguins)` observations and `r ncol(penguins)` variables. 
Each observation represents one penguin. Measurements include bill length, bill depth, and flipper length in millimeters, as well as body mass in grams.

Firstly, for the "species" variable, there are three different species, which are `r paste(unique(penguins$species), collapse = ", ")`. Secondly, "island" variable depicts three islands penguins inhabit, which are `r paste(unique(penguins$island), collapse = ", ") `. 

The mean of flipper length is `r round(mean(penguins$flipper_length_mm, na.rm = TRUE), 2)` mm, excluding missing values.

```{r problem1 scatter plot}
penguin_plot =  ggplot( data = penguins, mapping = aes(y = flipper_length_mm, x = bill_length_mm, color = species)) + geom_point()
penguin_plot
ggsave(
  file = "penguin_plot.png", 
  plot = penguin_plot, 
       )
```

# Problem 2

```{r problem2}
# Code for Problem 2
```