---
title: "P8105 Homework 1"
author: "Shiyu Kang"
output: github_document
---

# Problem 1

```{r problem1}
library(ggplot2)
library(tidyverse)
data("penguins", package = "palmerpenguins")
```
The penguins table contains `r nrow(penguins)` observations and `r ncol(penguins)` variables. 
Each observation represents one penguin. Measurements include bill length, bill depth, and flipper length in millimeters, as well as body mass in grams.

Firstly, for the "species" variable, there are three different species, which are `r paste(unique(penguins$species), collapse = ", ")`. Secondly, "island" variable depicts three islands penguins inhabit, which are `r paste(unique(penguins$island), collapse = ", ") `. 

The mean of flipper length is `r round(mean(penguins$flipper_length_mm, na.rm = TRUE), 2)` mm, excluding missing values.

```{r problem1 scatter plot}
penguin_plot =  ggplot( data = penguins, 
                        mapping = aes(y = flipper_length_mm, x = bill_length_mm, color = species)) + geom_point()
penguin_plot
ggsave(
  filename = "penguin_plot.png", 
  plot = penguin_plot, 
       )
```

# Problem 2
```{r problem2}
set.seed(42)
example_df = tibble(
 samp = rnorm(10),
 positive = samp > 0,
 text_label = c("a","b","c","d","e","f","g","h","i","j"),
 factor_label = factor(
   c("low","high","medium","low","low","high","low","high","medium","low"),
   levels = c("low","medium","high")
 )
)
mean(pull(example_df,samp))
mean(pull(example_df,positive))
mean(pull(example_df,text_label))
mean(pull(example_df,factor_label))
```

When calculating these 4 types of variables, we found that numeric and logical variable have the ouput of mean. For numeric, the mean is `r mean(pull(example_df,samp))`, it doesn't equal to 0 because it's generate based on 10 random observations. For logical, True = 1 and False = 0, so the mean will be a number within 0 and 1, which represents the proportion of True results.

For factor and character, return value is NA since mean() function cannot calculate directly under these 2 variables.

```{r numeric, results='hide', warning=FALSE}
as.numeric(pull(example_df,positive))
as.numeric(pull(example_df,text_label))
as.numeric(pull(example_df,factor_label))
```
We can know from the numeric switch that numeric, logical and factor variable can be expressed in numeric form. Logical has two values: 0 and 1. Factor label has three values: 1, 2, 3, corresponding to three different categories: low, medium and high. Character can't be expressed in numeric form, which results in a failure to calculate its mean. Although their mean can be calculated after conversion, it would be an average of category codes rather than a meaningful measurement.
