---
title: "P8105 Homework 1"
author: "Shiyu Kang"
output: github_document
---

# Problem 1

```{r problem1}
library(ggplot2)
data("penguins", package = "palmerpenguins")
```
The penguins table contains `r nrow(penguins)` observations and `r ncol(penguins)` variables. 
Each observation represents one penguin. Measurements include bill length, bill depth, and flipper length in millimeters, as well as body mass in grams.

Firstly, for the "species" variable, there are three different species, which are `r paste(unique(penguins$species), collapse = ", ")`. Secondly, "island" variable depicts three islands penguins inhabit, which are `r paste(unique(penguins$island), collapse = ", ") `. 

The mean of flipper length is `r round(mean(penguins$flipper_length_mm, na.rm = TRUE), 2)` mm, excluding missing values.

```{r problem1 scatter plot}
penguin_plot =  ggplot( data = penguins, 
                        mapping = aes(y = flipper_length_mm, x = bill_length_mm, color = species)) 
                + geom_point()
penguin_plot
ggsave(
  file = "penguin_plot.png", 
  plot = penguin_plot, 
       )
```

# Problem 2
```{r problem2}
set.seed(42)
example_df = tibble(
 samp = rnorm(10),
 positive = samp > 0,
 text_label = c("a","b","c","d","e","f","g","h","i","j"),
 factor_label = factor(
   c("low","high","medium","low","low","high","low","high","medium","low"),
   levels = c("low","medium","high")
 )
)
mean(pull(example_df,samp))
mean(pull(example_df,positive))
mean(pull(example_df,text_label))
mean(pull(example_df,factor_label))
```

When calculating these 4 types of variables, we found that numeric and logical variable have the ouput of mean. For numeric, the mean is `r mean(pull(example_df,samp))`, it doesn't equal to 0.5 because it's generate randomly based on the normal distribution. For logical, True = 1 and False = 0, so the mean will be a number within 0 and 1. 

For factor and character,  